Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-12-27 manuscript.Rmd
Add automatic calls for numbers of observations

@@

For both the target-only and the target and source data described above, time
series of the count of all events were generated by summing the total number of
events on each day, irrespective of ICEWS score. Similarly, time series of count
of positive events were generated by summing the number of ICEWS events for each
day that had an intensity rating greater than zero. Lastly, time series of count
of negative events were generated by summing the number of ICEWS events for each
day that had an intensity rating less than zero.

@@

### Syria as Source and Target
By adding Syria as a source in the data filtering, the event dataset increased in size
by N [fix number here] samples. These additional observations are times where Syria initiated
an event with another country. Events initiated by Syria but directed internally
within the country were already captured by the target-only filtering. Taking outwardly directed events into account dramatically changed the coupling between all events and social cohesion. There is no longer a significant number of shared trajectories or line lengths, indicating that the cohesion on Twitter is not tied to the frequency of overall daily events. Since source events are at the root of this difference, it is plausible that Syrians were focused on the target events as they are immediately impacting them, and the addition of the source events now overshadows the relationship between target events and social cohesion online. In contrast, there was a slight increase in coupling strength between positive events and social cohesion that once again can only be due to the externally directed events. These two time series showed greater stability in their coupling (reflected in L). But the significant ENTR metric suggests that there is more variability in the coupling, and thus we do not feel that the source events impacted the positive event coupling notably, but rather broke up the trajectories formed by the target events. Although the coupling between social cohesion with negative events were largely unchanged, there was a slight decrease in coupling strength (reflected in maxL) and increase in complexity of shared trajectories (reflected in rENTR). Similarly to that of positive events, this change may not be reflective of source events themselves, but rather a disruption of the relationship with target events.

>>>>

num_target <- sum(ICEWS_formatted_target$all_events_target)
num_source_target <- sum(ICEWS_formatted_source_target$all_events_source_target)

@@

For both the target-only (n = `r num_target`) and the target and source data (n = `r num_source_target`) described above, time
series of the count of all events were generated by summing the total number of
events on each day, irrespective of ICEWS score. Similarly, time series of count
of positive events were generated by summing the number of ICEWS events for each
day that had an intensity rating greater than zero. Lastly, time series of count
of negative events were generated by summing the number of ICEWS events for each
day that had an intensity rating less than zero.

@@

### Syria as Source and Target
By adding Syria as a source in the data filtering, the event dataset increased in size by `r num_source_target-num_target` samples. These additional observations are times where Syria initiated
an event with another country. Events initiated by Syria but directed internally
within the country were already captured by the target-only filtering. Taking outwardly directed events into account dramatically changed the coupling between all events and social cohesion. There is no longer a significant number of shared trajectories or line lengths, indicating that the cohesion on Twitter is not tied to the frequency of overall daily events. Since source events are at the root of this difference, it is plausible that Syrians were focused on the target events as they are immediately impacting them, and the addition of the source events now overshadows the relationship between target events and social cohesion online. In contrast, there was a slight increase in coupling strength between positive events and social cohesion that once again can only be due to the externally directed events. These two time series showed greater stability in their coupling (reflected in L). But the significant ENTR metric suggests that there is more variability in the coupling, and thus we do not feel that the source events impacted the positive event coupling notably, but rather broke up the trajectories formed by the target events. Although the coupling between social cohesion with negative events were largely unchanged, there was a slight decrease in coupling strength (reflected in maxL) and increase in complexity of shared trajectories (reflected in rENTR). Similarly to that of positive events, this change may not be reflective of source events themselves, but rather a disruption of the relationship with target events.
